Personal Total Income of Individual in the United States of America in 2023

### 2024-10-25 paper/paper.qmd
Re-run the model & Updated model results with new data

| Metric          | Value            |
|-----------------|------------------|
| Best Model MSE  | 6,057,654,880.33 |
| Best Model RMSE | 77,830.94        |
:::

@@

| Feature         | Importance |
|-----------------|------------|
| cat\_\_EDUC_new | 0.337465   |
| cat\_\_IND1990  | 0.243701   |
| num\_\_AGE      | 0.193615   |
| cat\_\_SEX      | 0.149471   |
| cat\_\_MARST    | 0.055754   |
| cat\_\_MORTGAGE | 0.012897   |
| cat\_\_SCHLTYPE | 0.004205   |
| cat\_\_VETSTAT  | 0.002891   |
| cat\_\_OWNERSHP | 0.000000   |
:::

@@

| Metric                         | Value            |
|--------------------------------|------------------|
| Mean Squared Error (MSE)       | 5,901,467,894.81 |
| Root Mean Squared Error (RMSE) | 76,821.01        |
:::

@@

| Metric                | Value     |
|-----------------------|-----------|
| Cross-Validation RMSE | 71,676.11 |
:::

>>>>

| Metric          | Value            |
|-----------------|------------------|
| Best Model MSE  | 6,057,429,750.02 |
| Best Model RMSE | 77,829.49        |
:::

@@

| Feature         | Importance |
|-----------------|------------|
| cat\_\_EDUC_new | 0.337065   |
| cat\_\_IND1990  | 0.243454   |
| num\_\_AGE      | 0.193926   |
| cat\_\_SEX      | 0.149342   |
| cat\_\_MARST    | 0.055948   |
| cat\_\_MORTGAGE | 0.013064   |
| cat\_\_SCHLTYPE | 0.004251   |
| cat\_\_VETSTAT  | 0.002948   |
| cat\_\_OWNERSHP | 0.000000   |
:::

@@

| Metric                         | Value            |
|--------------------------------|------------------|
| Mean Squared Error (MSE)       | 5,191,183,577.52 |
| Root Mean Squared Error (RMSE) | 72,049.87        |
:::

@@

| Metric                | Value     |
|-----------------------|-----------|
| Cross-Validation RMSE | 71,994.55 |
:::
